---
title: "Drought reshapes space use and intraguild overlap in an African large carnivore guild"
authored by: "Leigh West"
date: '2023-12-22'
output: pdf_document
---


This analysis examines if home range size, spatial overlap, and encounters for four large carnivore species (African wild dogs, lions, leopards, and cheetahs) in Botswana changes during drought conditions. Because each individual has different collar deployment lengths, in order to be able to make comparisons between them, I divided the data into monthly time periods in the wet and dry seasons each year. I then fit Brownian Bridge Movement Models to estimate home range area (in km squared) for each individual in each time period between 2011 and 2022 (95% and 50% isopleths). If there were multiple wild dog individuals from the same pack in one time period, I excluded all but one of them because the space use of the Pack is consistent across individuals. If there were multiple same-sex lion individuals in one time period, I excluded individuals with an overlap coefficient of > 0.7. I then estimated home range overlap using Bhattacharyya’s affinity metric, which produces an overlap coefficient between 0 and 1, with 1 representing perfect overlap. I proceed to analyze my data using the below modeling approach.

I used the Standard Precipitation Index (SPI) as a drought metric. I used two lagged SPIs, three months and annual, to test different hypotheses (effect of reduced surface water vs. broader ecologial effects, respectively). 

## Table of Contents

63: Home range models, 3-month Standard Precipitation Index
373: Home range models, annual Standard Precipitation Index
923: Overlap models
1386: Encounter models
1594: Figures


## Load necessary packages 

```{r packages, load packages include = FALSE}

options(stringsAsFactors = FALSE)
library(tidyverse)
library(dplyr)
library(glmmTMB)
library(DHARMa)
library(ggeffects)
library(RColorBrewer)
library(ggnewscale)
library(ggspatial)
library(ggplot2)

```


## Read in data

```{r csv files for analysis}

####Home range####

df_HR <- read.csv("home_range_table.csv")

####Overlap####

overlap_95_binom <- read.csv("overlap_95_binom.csv")
overlap_95_beta <- read.csv("overlap_95_beta.csv")
overlap_50_binom <- read.csv("overlap_50_binom.csv")
overlap_50_beta <- read.csv("overlap_50_beta.csv")

####Encounters####

encounters_200m <- read.csv("encounters_200m.csv")
encounters_400m <- read.csv("encounters_400m.csv")

```


## Home range models, three-month SPI 

```{r home range models 3-month}

#Wild dog 95% HR
dogmod95_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + (1|Pack), data=subset(df_HR, Species=="African Wild Dog" & isopleth=="BB95"), family = Gamma(link="log"))
summary(dogmod95_HR_3month)

#Wild Dog 50% HR
dogmod50_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + (1|Pack), data=subset(df_HR, Species=="African Wild Dog" & isopleth=="BB50"), family = Gamma(link="log"))
summary(dogmod50_HR_3month)


#Lion 95% HR
lionmod95_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + Sex + (1|Pack/id_simple), data=subset(df_HR, Species=="Lion" & isopleth=="BB95"), family = Gamma(link="log"))
summary(lionmod95_HR_3month)

#Lion 50% HR 
lionmod50_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + Sex + (1|Pack/id_simple), data=subset(df_HR, Species=="Lion" & isopleth=="BB50"), family = Gamma(link="log"))
summary(lionmod50_HR_3month)


#Leopard 95% HR
leopardmod95_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + (1|id_simple), data=subset(df_HR, Species=="Leopard" & isopleth=="BB95"), family = Gamma(link="log"))
summary(leopardmod95_HR_3month)

#Leopard 50% HR 
leopardmod50_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + (1|id_simple), data=subset(df_HR, Species=="Leopard" & isopleth=="BB50"), family = Gamma(link="log"))
summary(leopardmod50_HR_3month)


#Cheetah 95% HR
cheetahmod95_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + Sex + (1|id_simple), data=subset(df_HR, Species=="Cheetah" & isopleth=="BB95"), family = Gamma(link="log"))
summary(cheetahmod95_HR_3month)

#Cheetah 50% HR 
cheetahmod50_HR_3month <- glmmTMB(hr_area ~ threemonth_spi + Sex + (1|id_simple), data=subset(df_HR, Species=="Cheetah" & isopleth=="BB50"), family = Gamma(link="log"))
summary(cheetahmod50_HR_3month)


```


## Bootstrap confidence intervals for each model

```{r Bootstrap CIs 3-month home range models}

#Wild dog 95% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(dogmod95_HR_3month))
  bmod <- update(dogmod95_HR_3month, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_dog95_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Wild dog 50% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(dogmod50_HR_3month))
  bmod <- update(dogmod50_HR_3month, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_dog50_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Lion 95% home range
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA, 2, nb)
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(lionmod95_HR_3month))
    bmod <- update(lionmod95_HR_3month, ynew ~ .)
    coefmat[, i] <- summary(bmod)$coefficients$cond[1:2, 1]
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_lion95_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Lion 50% home range
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA, 2, nb)
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(lionmod50_HR_3month))
    bmod <- update(lionmod50_HR_3month, ynew ~ .)
    coefmat[, i] <- summary(bmod)$coefficients$cond[1:2, 1]
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_lion50_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Leopard 95% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(leopardmod95_HR_3month))
  bmod <- update(leopardmod95_HR_3month, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_leopard95_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Leopard 50% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(leopardmod50_HR_3month))
  bmod <- update(leopardmod50_HR_3month, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_leopard50_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Cheetah 95% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(cheetahmod95_HR_3month))
  bmod <- update(cheetahmod95_HR_3month, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[1:2,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_cheetah95_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Cheetah 50% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(cheetahmod50_HR_3month))
  bmod <- update(cheetahmod50_HR_3month, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[1:2,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_cheetah50_3month <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


``` 


## Predicting from models and bootstrap CIs on predictions

```{r predictions and CIs 3-month home range models}

#Wild dog 95% HR

#Creating new data set to predict from where x values are bounded by minimum and maximum SPI values found in observed data
original_vec <- c(-1.2, 0, 1.7)
spi_values_new <- seq(original_vec[1], original_vec[length(original_vec)], by = 0.1)
spi_values_new_rounded <- round(spi_values_new, digits = 2)

data.n <- data.frame(threemonth_spi = spi_values_new_rounded)

set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
for(i in 1:boots){
  ynew <- unlist(simulate(dogmod95_HR_3month))
  ymod <- update(dogmod95_HR_3month,ynew ~ .)
  RE.sd <- sqrt(VarCorr(ymod)$cond$Pack[1]) 
  yest[,i] <- exp(predict(ymod, re.form = ~0, newdata = data.n) + rnorm(1,0,RE.sd))  #for log link 
}

#this will give me the mean and the confidence intervals for each of my input variable levels 
mean_pred_dog95_3month <- apply(yest,1,mean)
pred_dog95_3month <- cbind(data.n, mean_pred_dog95_3month)
CIs_pred_dog95_3month <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})



#Wild dog 50% HR

data.n <- data.frame(threemonth_spi = spi_values_new_rounded)

set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
for(i in 1:boots){
  ynew <- unlist(simulate(dogmod50_HR_3month))
  ymod <- update(dogmod50_HR_3month,ynew ~ .)
  RE.sd <- sqrt(VarCorr(ymod)$cond$Pack[1]) 
  yest[,i] <- exp(predict(ymod, re.form = ~0, newdata = data.n) + rnorm(1,0,RE.sd))  #for log link 
}

#this will give me the mean and the confidence intervals for each of my input variable levels 
mean_pred_dog50_3month <- apply(yest,1,mean)
pred_dog50_3month <- cbind(data.n, mean_pred_dog50_3month)
CIs_pred_dog50_3month <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})


```


## Diagnostic plots for home range models, three-month SPI

For some of these models, significant deviations were detected in my plot of residual vs. predicated values, indicating I violated the assumption of identically distributed errors. Overall, I thought the diagnostic plots looked reliable enough to move forward with making inference from these models.

```{r DHARMa plots 3-month home range models}

#Wild dog 95% HR
dogmod95_HR_3month_simres <- simulateResiduals(dogmod95_HR_3month)
plot(dogmod95_HR_3month_simres)

#Wild Dog 50% HR
dogmod50_HR_3month_simres <- simulateResiduals(dogmod50_HR_3month)
plot(dogmod50_HR_3month_simres)


#Lion 95% HR
lionmod95_HR_3month_simres <- simulateResiduals(lionmod95_HR_3month)
plot(lionmod95_HR_3month_simres)

#Lion 50% HR 
lionmod50_HR_3month_simres <- simulateResiduals(lionmod50_HR_3month)
plot(lionmod50_HR_3month_simres)


#Leopard 95% HR
leopardmod95_HR_3month_simres <- simulateResiduals(leopardmod95_HR_3month)
plot(leopardmod95_HR_3month_simres)

#Leopard 50% HR 
leopardmod50_HR_3month_simres <- simulateResiduals(leopardmod50_HR_3month)
plot(leopardmod50_HR_3month_simres)


#Cheetah 95% HR
cheetahmod95_HR_3month_simres <- simulateResiduals(cheetahmod95_HR_3month)
plot(cheetahmod95_HR_3month_simres)

#Cheetah 50% HR 
cheetahmod50_HR_3month_simres <- simulateResiduals(cheetahmod50_HR_3month)
plot(cheetahmod50_HR_3month_simres)

```


## Home range models, annual SPI 

```{r home range models annual}

#Wild dog 95% HR
dogmod95_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + (1|Pack), data=subset(df_HR, Species=="African Wild Dog" & isopleth=="BB95"), family = Gamma(link="log"))
summary(dogmod95_HR_annual)

#Wild Dog 50% HR
dogmod50_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + (1|Pack), data=subset(df_HR, Species=="African Wild Dog" & isopleth=="BB50"), family = Gamma(link="log"))
summary(dogmod50_HR_annual)


#Lion 95% HR
lionmod95_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + Sex + (1|Pack/id_simple), data=subset(df_HR, Species=="Lion" & isopleth=="BB95"), family = Gamma(link="log"))
summary(lionmod95_HR_annual)

#Lion 50% HR 
lionmod50_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + Sex + (1|Pack/id_simple), data=subset(df_HR, Species=="Lion" & isopleth=="BB50"), family = Gamma(link="log"))
summary(lionmod50_HR_annual)


#Leopard 95% HR
leopardmod95_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + (1|id_simple), data=subset(df_HR, Species=="Leopard" & isopleth=="BB95"), family = Gamma(link="log"))
summary(leopardmod95_HR_annual)

#Leopard 50% HR 
leopardmod50_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + (1|id_simple), data=subset(df_HR, Species=="Leopard" & isopleth=="BB50"), family = Gamma(link="log"))
summary(leopardmod50_HR_annual)


#Cheetah 95% HR
cheetahmod95_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + Sex + (1|id_simple), data=subset(df_HR, Species=="Cheetah" & isopleth=="BB95"), family = Gamma(link="log"))
summary(cheetahmod95_HR_annual)

#Cheetah 50% HR 
cheetahmod50_HR_annual <- glmmTMB(hr_area ~ prevyear_spi + Sex + (1|id_simple), data=subset(df_HR, Species=="Cheetah" & isopleth=="BB50"), family = Gamma(link="log"))
summary(cheetahmod50_HR_annual)

```


## Bootstrap confidence intervals for each model

```{r bootstrap CIs annual home range models}

#Wild dog 95% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(dogmod95_HR_annual))
  bmod <- update(dogmod95_HR_annual, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_dog95_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Wild dog 50% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(dogmod50_HR_annual))
  bmod <- update(dogmod50_HR_annual, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_dog50_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Lion 95% home range

#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA, 2, nb)
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(lionmod95_HR_annual))
    bmod <- update(lionmod95_HR_annual, ynew ~ .)
    coefmat[, i] <- summary(bmod)$coefficients$cond[1:2, 1]
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_lion95_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Lion 50% home range
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA, 2, nb)
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(lionmod50_HR_annual))
    bmod <- update(lionmod50_HR_annual, ynew ~ .)
    coefmat[, i] <- summary(bmod)$coefficients$cond[1:2, 1]
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_lion50_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Leopard 95% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(leopardmod95_HR_annual))
  bmod <- update(leopardmod95_HR_annual, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_leopard95_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Leopard 50% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(leopardmod50_HR_annual))
  bmod <- update(leopardmod50_HR_annual, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_leopard50_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Cheetah 95% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(cheetahmod95_HR_annual))
  bmod <- update(cheetahmod95_HR_annual, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[1:2,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_cheetah95_annual <-t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Cheetah 50% home range

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,2,nb) 
for(i in 1:nb){
  ynew <- unlist(simulate(cheetahmod50_HR_annual))
  bmod <- update(cheetahmod50_HR_annual, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[1:2,1]
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[1:2,1])
coefmat <- data.frame(coefmat)
CIs_cheetah50_annual <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


``` 


## Predicting from models and bootstrap CIs on predictions

```{r model predictions and CIs annual home range models}

#Lion 95% HR
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

data.n <- data.frame(prevyear_spi = rep(spi_values_new_rounded,2),Sex = c(rep("M",30),rep("F",30)))

set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
i <- 1
while (i <= boots) {
  result <- tryCatch({
    ynew <- unlist(simulate(lionmod95_HR_annual))
    ymod <- update(lionmod95_HR_annual, ynew ~ .)
    RE.sd <- sqrt(VarCorr(ymod)$cond$`id_simple:Pack`[1])
    exp_pred <- exp(predict(ymod, re.form = ~0, allow.new.levels = TRUE, newdata = data.n) + rnorm(1, 0, RE.sd))
    
    if (!any(is.na(exp_pred))) {
      yest[, i] <- exp_pred
      i <- i + 1  # Only increment i if the iteration is successful
    }
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })
  
  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

mean_pred_lion95_annual <- apply(yest,1,mean)
pred_lion95_annual <- cbind(data.n, mean_pred_lion95_annual)
CIs_pred_lion95_annual <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})

#Lion 50% HR
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

data.n <- data.frame(prevyear_spi = rep(spi_values_new_rounded,2),Sex = c(rep("M",30),rep("F",30)))

set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
i <- 1
while (i <= boots) {
  result <- tryCatch({
    ynew <- unlist(simulate(lionmod50_HR_annual))
    ymod <- update(lionmod50_HR_annual, ynew ~ .)
    RE.sd <- sqrt(VarCorr(ymod)$cond$`id_simple:Pack`[1])
    exp_pred <- exp(predict(ymod, re.form = ~0, allow.new.levels = TRUE, newdata = data.n) + rnorm(1, 0, RE.sd))
    
    if (!any(is.na(exp_pred))) {
      yest[, i] <- exp_pred
      i <- i + 1  # Only increment i if the iteration is successful
    }
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })
  
  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

mean_pred_lion50_annual <- apply(yest,1,mean)
pred_lion50_annual <- cbind(data.n, mean_pred_lion50_annual)
CIs_pred_lion50_annual <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})


#Leopard 95% HR

data.n <- data.frame(prevyear_spi = spi_values_new_rounded)

set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
for(i in 1:boots){
  ynew <- unlist(simulate(leopardmod95_HR_annual))
  ymod <- update(leopardmod95_HR_annual,ynew ~ .)
  RE.sd <- sqrt(VarCorr(ymod)$cond$`id_simple`[1])
  yest[,i] <- exp(predict(ymod, re.form = ~0, allow.new.levels = TRUE, newdata = data.n) + rnorm(1,0,RE.sd)) 
}

mean_pred_leopard95_annual <- apply(yest,1,mean)
pred_leopard95_annual <- cbind(data.n, mean_pred_leopard95_annual)
CIs_pred_leopard95_annual <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})


#Leopard 50% HR

data.n <- data.frame(prevyear_spi = spi_values_new_rounded)

set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
for(i in 1:boots){
  ynew <- unlist(simulate(leopardmod50_HR_annual))
  ymod <- update(leopardmod50_HR_annual,ynew ~ .)
  RE.sd <- sqrt(VarCorr(ymod)$cond$`id_simple`[1])
  yest[,i] <- exp(predict(ymod, re.form = ~0, allow.new.levels = TRUE, newdata = data.n) + rnorm(1,0,RE.sd)) 
}

mean_pred_leopard50_annual <- apply(yest,1,mean)
pred_leopard50_annual <- cbind(data.n, mean_pred_leopard50_annual)
CIs_pred_leopard50_annual <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})


```


## Diagnostic plots for home range models, annual SPI

For some of these models, significant deviations were detected in my plot of residual vs. predicated values, indicating I violated the assumption of identically distributed errors. Overall, I thought the diagnostic plots looked reliable enough to move forward with making inference from these models.

```{r DHARMa plots annual home range models}

#Wild dog 95% HR
dogmod95_HR_annual_simres <- simulateResiduals(dogmod95_HR_annual)
plot(dogmod95_HR_annual_simres)

#Wild Dog 50% HR
dogmod50_HR_annual_simres <- simulateResiduals(dogmod50_HR_annual)
plot(dogmod50_HR_annual_simres)


#Lion 95% HR
lionmod95_HR_annual_simres <- simulateResiduals(lionmod95_HR_annual)
plot(lionmod95_HR_annual_simres)

#Lion 50% HR 
lionmod50_HR_annual_simres <- simulateResiduals(lionmod50_HR_annual)
plot(lionmod50_HR_annual_simres)


#Leopard 95% HR
leopardmod95_HR_annual_simres <- simulateResiduals(leopardmod95_HR_annual)
plot(leopardmod95_HR_annual_simres)

#Leopard 50% HR 
leopardmod50_HR_annual_simres <- simulateResiduals(leopardmod50_HR_annual)
plot(leopardmod50_HR_annual_simres)


#Cheetah 95% HR
cheetahmod95_HR_annual_simres <- simulateResiduals(cheetahmod95_HR_annual)
plot(cheetahmod95_HR_annual_simres)

#Cheetah 50% HR 
cheetahmod50_HR_annual_simres <- simulateResiduals(cheetahmod50_HR_annual)
plot(cheetahmod50_HR_annual_simres)

```


## Test for temporal autocorrelation in home range models

```{r acf() function 3-month and annual home range models}

acf(resid(dogmod95_HR_3month))
acf(resid(dogmod95_HR_annual))
acf(resid(dogmod50_HR_3month))
acf(resid(dogmod50_HR_annual))


acf(resid(lionmod95_HR_3month))
acf(resid(lionmod95_HR_annual))
acf(resid(lionmod50_HR_3month))
acf(resid(lionmod50_HR_annual))


acf(resid(leopardmod95_HR_3month))
acf(resid(leopardmod95_HR_annual))
acf(resid(leopardmod50_HR_3month))
acf(resid(leopardmod50_HR_annual))


acf(resid(cheetahmod95_HR_3month))
acf(resid(cheetahmod95_HR_annual))
acf(resid(cheetahmod50_HR_3month))
acf(resid(cheetahmod50_HR_annual))

```


## Calculate percent change in home range across most extreme SPI values

Percent change between home range sizes at the 25th and 75th SPI percentiles.

25th percentile SPI value = -0.5
75th percentile SPI value = 1

```{r percent change in home range models with significant results}

#Wild dog

#95%
twentyfive_percentile_dog95_HR_3month_predictions <- subset(pred_dog95_3month, threemonth_spi == -0.5)
#244.0326

seventyfive_percentile_dog95_HR_3month_predictions <- subset(pred_dog95_3month, threemonth_spi == 1)
#180.0469

#Percent change dog 95
((twentyfive_percentile_dog95_HR_3month_predictions[,2] - seventyfive_percentile_dog95_HR_3month_predictions[,2]) / seventyfive_percentile_dog95_HR_3month_predictions[,2])*100
#35.53835

#50%
twentyfive_percentile_dog50_HR_3month_predictions <- subset(pred_dog50_3month, threemonth_spi == -0.5)
#31.83327

seventyfive_percentile_dog50_HR_3month_predictions <- subset(pred_dog50_3month, threemonth_spi == 1)
#19.344

#Percent change dog 50
((twentyfive_percentile_dog50_HR_3month_predictions[,2] - seventyfive_percentile_dog50_HR_3month_predictions[,2]) / seventyfive_percentile_dog50_HR_3month_predictions[,2])*100
#64.56405

#Lion

#95%
twentyfive_percentile_lion95_HR_3month_predictions <- subset(pred_lion95_annual, prevyear_spi == -0.5)
#Male: 117.52595
#Female: 81.89874

seventyfive_percentile_lion95_HR_3month_predictions <- subset(pred_lion95_annual, prevyear_spi == 1)
#Male: 76.67691
#Female: 53.37165

#Percent change lion 95

#Male
((twentyfive_percentile_lion95_HR_3month_predictions[1,3] - seventyfive_percentile_lion95_HR_3month_predictions[1,3]) / seventyfive_percentile_lion95_HR_3month_predictions[1,3])*100
#53.27424

#Female
((twentyfive_percentile_lion95_HR_3month_predictions[2,3] - seventyfive_percentile_lion95_HR_3month_predictions[2,3]) / seventyfive_percentile_lion95_HR_3month_predictions[2,3])*100

#53.44989

#50%
twentyfive_percentile_lion50_HR_3month_predictions <- subset(pred_lion50_annual, prevyear_spi == -0.5)
#Male: 9.814067
#Female: 8.231975

seventyfive_percentile_lion50_HR_3month_predictions <- subset(pred_lion50_annual, prevyear_spi == 1)
#Male: 7.376284
#Female: 6.171774


#Percent change lion 50

#Male
((twentyfive_percentile_lion50_HR_3month_predictions[1,3] - seventyfive_percentile_lion50_HR_3month_predictions[1,3]) / seventyfive_percentile_lion50_HR_3month_predictions[1,3])*100
#33.04893

#Female
((twentyfive_percentile_lion50_HR_3month_predictions[2,3] - seventyfive_percentile_lion50_HR_3month_predictions[2,3]) / seventyfive_percentile_lion50_HR_3month_predictions[2,3])*100
#33.38102

#Leopard

#95%
twentyfive_percentile_leopard95_HR_3month_predictions <- subset(pred_leopard95_annual, prevyear_spi == -0.5)
#71.38628

seventyfive_percentile_leopard95_HR_3month_predictions <- subset(pred_leopard95_annual, prevyear_spi == 1)
#42.93292

#Percent change leopard 95
((twentyfive_percentile_leopard95_HR_3month_predictions[,2] - seventyfive_percentile_leopard95_HR_3month_predictions[,2]) / seventyfive_percentile_leopard95_HR_3month_predictions[,2])*100
#66.27399

#50%
twentyfive_percentile_leopard50_HR_3month_predictions <- subset(pred_leopard50_annual, prevyear_spi == -0.5)
#13.42828

seventyfive_percentile_leopard50_HR_3month_predictions <- subset(pred_leopard50_annual, prevyear_spi == 1)
#4.08824


#Percent change leopard 50
((twentyfive_percentile_leopard50_HR_3month_predictions[,2] - seventyfive_percentile_leopard50_HR_3month_predictions[,2]) / seventyfive_percentile_leopard50_HR_3month_predictions[,2])*100
#228.4611


```


## Calculate predicted home range at SPI = 0 ('average' conditions) for significant results

```{r home range size during average conditions}

#Wild dog 3-month SPI

#95%
HR_dog95_avg_conditions <- subset(pred_dog95_3month, threemonth_spi == 0)
#220.3813

#50%
HR_dog50_avg_conditions <- subset(pred_dog50_3month, threemonth_spi == 0)
#26.92303

#Lion annual SPI

#95%
HR_lion95_avg_conditions <- subset(pred_lion95_annual, prevyear_spi == 0)
#Male - 101.81612
#Female - 70.92368

#50%
HR_lion50_avg_conditions <- subset(pred_lion50_annual, prevyear_spi == 0)
#Male - 8.899139
#Female - 7.458075

#Leopard annual SPI

#95%
HR_leopard95_avg_conditions <- subset(pred_leopard95_annual, prevyear_spi == 0)
#59.95194

#50%
HR_leopard50_avg_conditions <- subset(pred_leopard50_annual, prevyear_spi == 0)
#8.924351

```


## Overlap models (mixture model; bernoulli & beta distributions)

My overlap models are mixture models, with each treatment (SPI / isopleth combo) having a bernoulli model to test a binary response of was there (1) or was there not (0) overlap between two species, and a beta model to test whether, for those species that had overlap > 0, SPI had an effect on degree of overlap.

```{r overlap models 3-month}

#Overlap of 95% home ranges

#Bernoulli model
allsp95_overlap_3month_binom <- glmmTMB(overlap_binary ~ dyad_species + threemonth_spi:dyad_species + (1|dyad_id), data=overlap_95_binom, family = binomial(link = "logit"))
summary(allsp95_overlap_3month_binom)

#Beta model
allsp95_overlap_3month_beta <- glmmTMB(overlap ~ dyad_species + threemonth_spi:dyad_species + (1|dyad_id), data=overlap_95_beta, family = beta_family(link = "logit"))
summary(allsp95_overlap_3month_beta)


#Overlap of 50% home ranges

#Bernoulli model
allsp50_overlap_3month_binom <- glmmTMB(overlap_binary ~ dyad_species + threemonth_spi:dyad_species + (1|dyad_id), data=overlap_50_binom, binomial(link = "logit"))
summary(allsp50_overlap_3month_binom)

#Beta model
allsp50_overlap_3month_beta <- glmmTMB(overlap ~ dyad_species + threemonth_spi:dyad_species + (1|dyad_id), data=overlap_50_beta, family = beta_family(link = "logit"))
summary(allsp50_overlap_3month_beta)


```


```{r overlap models annual}

#Overlap of 95% home ranges

#Bernoulli model
allsp95_overlap_annual_binom <- glmmTMB(overlap_binary ~ dyad_species + prevyear_spi:dyad_species + (1|dyad_id), data=overlap_95_binom, family = binomial(link = "logit"))
summary(allsp95_overlap_annual_binom)

#Beta model
allsp95_overlap_annual_beta <- glmmTMB(overlap ~ dyad_species + prevyear_spi:dyad_species + (1|dyad_id), data=overlap_95_beta, family = beta_family(link = "logit"))
summary(allsp95_overlap_annual_beta)


#Overlap of 50% home ranges

#Bernoulli model
allsp50_overlap_annual_binom <- glmmTMB(overlap_binary ~ dyad_species + prevyear_spi:dyad_species + (1|dyad_id), data=overlap_50_binom, family = binomial(link = "logit"))
summary(allsp50_overlap_annual_binom)

#Beta model
allsp50_overlap_annual_beta <- glmmTMB(overlap ~ dyad_species + prevyear_spi:dyad_species + (1|dyad_id), data=overlap_50_beta, family = beta_family(link = "logit"))
summary(allsp50_overlap_annual_beta)

```


## Bootstrap confidence intervals for each model

```{r Bootstrap CIs overlap models}

#3-month SPI

#95% home range overlap bernoulli
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,12,nb) 
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(allsp95_overlap_3month_binom))[1:nrow(overlap_95_binom)] 
    bmod <- update(allsp95_overlap_3month_binom, ynew ~ .) 
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_95_3monthBinom <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#95% home range overlap beta

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,12,nb) #Not sure what to put as second argument here
for(i in 1:nb){
  ynew <- unlist(simulate(allsp95_overlap_3month_beta))[1:nrow(overlap_95_beta)] 
  bmod <- update(allsp95_overlap_3month_beta, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_95_3monthBeta <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#50% home range overlap bernoulli
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,10,nb) 
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(allsp50_overlap_3month_binom))[1:nrow(overlap_50_binom)] 
    bmod <- update(allsp50_overlap_3month_binom, ynew ~ .) 
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1]  
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}


rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_50_3monthBinom <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#50% home range overlap beta

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,6,nb) #Not sure what to put as second argument here
for(i in 1:nb){
  ynew <- unlist(simulate(allsp50_overlap_3month_beta))[1:nrow(overlap_50_beta)] 
  bmod <- update(allsp50_overlap_3month_beta, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_50_3monthBeta <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



#Annual SPI


#95% home range overlap bernoulli
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,12,nb) 
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(allsp95_overlap_annual_binom))[1:nrow(overlap_95_binom)] 
    bmod <- update(allsp95_overlap_annual_binom, ynew ~ .) 
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_95_annualBinom <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#95% home range overlap beta

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,12,nb) #Not sure what to put as second argument here
for(i in 1:nb){
  ynew <- unlist(simulate(allsp95_overlap_annual_beta))[1:nrow(overlap_95_beta)] 
  bmod <- update(allsp95_overlap_annual_beta, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_95_annualBeta <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#50% home range overlap bernoulli
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,10,nb) 
i <- 1

while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(allsp50_overlap_annual_binom))[1:nrow(overlap_50_binom)] 
    bmod <- update(allsp50_overlap_annual_binom, ynew ~ .) 
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_50_annualBinom <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#50% home range overlap beta

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,6,nb) #Not sure what to put as second argument here
for(i in 1:nb){
  ynew <- unlist(simulate(allsp50_overlap_annual_beta))[1:nrow(overlap_50_beta)] 
  bmod <- update(allsp50_overlap_annual_beta, ynew ~ .) 
  coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])
coefmat <- data.frame(coefmat)
CIs_50_annualBeta <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


``` 


## Predictions and CIs

```{r model predictions and CIs overlap models}

##Annual SPI

#95% Overlap annual beta

#Creating dataframe to populate
data.n.dle <- data.frame(dyad_species = "Dog-Leopard", prevyear_spi = spi_values_new_rounded)
data.n.cli <- data.frame(dyad_species = "Cheetah-Lion", prevyear_spi = spi_values_new_rounded)
data.n.dli <- data.frame(dyad_species = "Dog-Lion", prevyear_spi = spi_values_new_rounded)
data.n.cd <- data.frame(dyad_species = "Cheetah-Dog", prevyear_spi = spi_values_new_rounded)
data.n.cle <- data.frame(dyad_species = "Cheetah-Leopard", prevyear_spi = spi_values_new_rounded)
data.n.leli <- data.frame(dyad_species = "Leopard-Lion", prevyear_spi = spi_values_new_rounded)
data.n <- rbind(data.n.dle, data.n.cli, data.n.dli, data.n.cd, data.n.cle, data.n.leli)


set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
for(i in 1:boots){
  ynew <- unlist(simulate(allsp95_overlap_annual_beta))
  ymod <- update(allsp95_overlap_annual_beta,ynew ~ .)
  RE.sd <- sqrt(VarCorr(ymod)$cond$dyad_id[1]) 
  yest[,i] <- 1/ (1+exp(-(predict(ymod, re.form = ~0, newdata = data.n) + rnorm(1,0,RE.sd))))
}



#this will give me the mean and the confidence intervals for each of my input variable levels 
mean_pred_overlap95_beta_annual <- apply(yest,1,mean)
pred_overlap95_beta_annual <- cbind(data.n, mean_pred_overlap95_beta_annual)
CIs_pred_overlap95_beta_annual <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})



#50% Overlap annual beta

#Creating dataframe to populate
data.n.cli <- data.frame(dyad_species = "Cheetah-Lion", prevyear_spi = spi_values_new_rounded)
data.n.dli <- data.frame(dyad_species = "Dog-Lion", prevyear_spi = spi_values_new_rounded)
data.n.leli <- data.frame(dyad_species = "Leopard-Lion", prevyear_spi = spi_values_new_rounded)
data.n <- rbind(data.n.cli, data.n.dli, data.n.leli)


set.seed(1)
boots <- 1000
yest <- matrix(NA,nrow(data.n),ncol=boots)
for(i in 1:boots){
  ynew <- unlist(simulate(allsp50_overlap_annual_beta))
  ymod <- update(allsp50_overlap_annual_beta,ynew ~ .)
  RE.sd <- sqrt(VarCorr(ymod)$cond$dyad_id[1]) 
  yest[,i] <- 1/ (1+exp(-(predict(ymod, re.form = ~0, newdata = data.n) + rnorm(1,0,RE.sd))))
}

#this will give me the mean and the confidence intervals for each of my input variable levels 
mean_pred_overlap50_beta_annual <- apply(yest,1,mean)
pred_overlap50_beta_annual <- cbind(data.n, mean_pred_overlap50_beta_annual)
CIs_pred_overlap50_beta_annual <- apply(yest,1,function(x){quantile(x,probs=c(0.025,0.975))})



```


## Diagnostic plots for overlap models

```{r DHARMa plots 3-month SPI}

#overlap of 95% home ranges

#Bernoulli model
allsp95_overlap_3month_binom_simres <- simulateResiduals(allsp95_overlap_3month_binom)
plot(allsp95_overlap_3month_binom_simres)

#Beta model
allsp95_overlap_3month_beta_simres <- simulateResiduals(allsp95_overlap_3month_beta)
plot(allsp95_overlap_3month_beta_simres)



#overlap of 50% home ranges

#Bernoulli model
allsp50_overlap_3month_binom_simres <- simulateResiduals(allsp50_overlap_3month_binom)
plot(allsp50_overlap_3month_binom_simres)

#Beta model
allsp95_overlap_3month_beta_simres <- simulateResiduals(allsp95_overlap_3month_beta)
plot(allsp95_overlap_3month_beta_simres)

```


```{r DHARMa plots annual SPI}

#overlap of 95% home ranges

#Bernoulli model
allsp95_overlap_annual_binom_simres <- simulateResiduals(allsp95_overlap_annual_binom)
plot(allsp95_overlap_annual_binom_simres)

#Beta model
allsp95_overlap_annual_beta_simres <- simulateResiduals(allsp95_overlap_annual_beta)
plot(allsp95_overlap_annual_beta_simres)



#overlap of 50% home ranges

#Bernoulli model
allsp50_overlap_annual_binom_simres <- simulateResiduals(allsp50_overlap_annual_binom)
plot(allsp50_overlap_annual_binom_simres)

#Beta model
allsp50_overlap_annual_beta_simres <- simulateResiduals(allsp50_overlap_annual_beta)
plot(allsp50_overlap_annual_beta_simres)

```


## Test for temporal autocorrelation in overlap models

```{r acf() function for 3-month and annual overlap models}

acf(resid(allsp95_overlap_annual_binom))
acf(resid(allsp95_overlap_annual_beta))
acf(resid(allsp50_overlap_annual_binom))
acf(resid(allsp50_overlap_annual_beta))

acf(resid(allsp95_overlap_3month_binom))
acf(resid(allsp95_overlap_3month_beta))
acf(resid(allsp50_overlap_3month_binom))
acf(resid(allsp50_overlap_3month_beta))


```


## Calculate percent change in predicted overlap across most extreme observed SPI values

Percent change between home range sizes at the 25th and 75th SPI percentiles.

25th percentile SPI value = -0.5
75th percentile SPI value = 1

```{r percent change in beta overlap models with significant results}

#Cheetah-Lion

cheetahlion_overlap_annual_predictions <- subset(pred_overlap95_beta_annual, dyad_species == "Cheetah-Lion")

twentyfive_percentile_cheetahlion_overlap_annual_predictions <- subset(cheetahlion_overlap_annual_predictions, prevyear_spi == -0.5)
#0.2072713

seventyfive_percentile_cheetahlion_overlap_annual_predictions <- subset(cheetahlion_overlap_annual_predictions, prevyear_spi == 1)
#0.09476242

#Percent change 
(twentyfive_percentile_cheetahlion_overlap_annual_predictions[,2] - seventyfive_percentile_cheetahlion_overlap_annual_predictions[,2])/seventyfive_percentile_cheetahlion_overlap_annual_predictions[,2]*100
#118.7273


#Leopard-Lion

leopardlion_overlap_annual_predictions <- subset(pred_overlap50_beta_annual, dyad_species == "Leopard-Lion")

twentyfive_percentile_leopardlion_overlap_annual_predictions <- subset(leopardlion_overlap_annual_predictions, prevyear_spi == -0.5)
#0.1093595

seventyfive_percentile_leopardlion_overlap_annual_predictions <- subset(leopardlion_overlap_annual_predictions, prevyear_spi == 1)
#0.06144436

#Percent change dog 95
(twentyfive_percentile_leopardlion_overlap_annual_predictions[,2] - seventyfive_percentile_leopardlion_overlap_annual_predictions[,2])/seventyfive_percentile_leopardlion_overlap_annual_predictions[,2]*100
#77.98135


```


## Calculate predicted overlap coefficient at SPI = 0 ('average' conditions) for significant results

```{r beta overlap during average conditions}

#Cheetah-Lion dog annual SPI beta

cheetahlion_overlap_avg_conditions <- subset(cheetahlion_overlap_annual_predictions, prevyear_spi == 0)


#Lion-Leopard annual SPI beta


leopardlion_overlap_avg_conditions <- subset(leopardlion_overlap_annual_predictions, prevyear_spi == 0)

```


## Encounter models

Number of encounters per year-month is the repsonse, with SPI and species dyad nested within spi as fixed effects, and individual-level dyad id as a random effect.

```{r 200m encounter radius models}

encounters_mod_3month_200m <- glmmTMB(number_encounters ~ dyad_species + threemonth_spi:dyad_species + (1|dyad_id), data=encounters_200m, family = truncated_poisson(link = "log"))
summary(encounters_mod_3month_200m)

encounters_mod_annual_200m <- glmmTMB(number_encounters ~ dyad_species + prevyear_spi:dyad_species + (1|dyad_id), data=encounters_200m, family = truncated_poisson(link = "log"))
summary(encounters_mod_annual_200m)

```


```{r 400m encounter radius models}

encounters_mod_3month_400m <- glmmTMB(number_encounters ~ dyad_species + threemonth_spi:dyad_species + (1|dyad_id), data=encounters_400m, family = truncated_poisson(link = "log"))
summary(encounters_mod_3month_400m)

encounters_mod_annual_400m <- glmmTMB(number_encounters ~ dyad_species + prevyear_spi:dyad_species + (1|dyad_id), data=encounters_400m, family = truncated_poisson(link = "log"))
summary(encounters_mod_annual_400m)

```


## Bootstrap confidence intervals for each encounter model

```{r Bootstrap CIs 200m encounters}

#Encounters 3month 
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,8,nb) 
i <- 1
while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(encounters_mod_3month_200m)) 
    bmod <- update(encounters_mod_3month_200m, ynew ~ .)  
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])  #Not sure what row names would be here
coefmat <- data.frame(coefmat)
CIs_3month_encounter200 <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Encounters annual
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence and optimization errors


set.seed(1)
nb <- 1000
coefmat <- matrix(NA,8,nb) 
i <- 1
while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(encounters_mod_annual_200m)) 
    bmod <- update(encounters_mod_annual_200m, ynew ~ .)  
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}


rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])  #Not sure what row names would be here
coefmat <- data.frame(coefmat)
CIs_annual_encounter200 <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


``` 


```{r Bootstrap CIs 400m encounters}

#Encounters 3month 

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,8,nb) 
i <- 1
while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(encounters_mod_3month_400m)) 
    bmod <- update(encounters_mod_3month_400m, ynew ~ .)  
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])  #Not sure what row names would be here
coefmat <- data.frame(coefmat)
CIs_3month_encounter400 <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))


#Encounters annual
#A 'while loop' is used instead of a 'for loop' in order to exclude model runs with convergence and optimization errors

set.seed(1)
nb <- 1000
coefmat <- matrix(NA,8,nb) 
i <- 1
while (i <= nb) {
  result <- tryCatch({
    ynew <- unlist(simulate(encounters_mod_annual_400m)) 
    bmod <- update(encounters_mod_annual_400m, ynew ~ .)  
    coefmat[,i] <- summary(bmod)$coefficients$cond[,1] 
    i <- i + 1  # Only increment i if the iteration is successful
  }, warning = function(w) {
    cat("Warning in iteration", i, ":", w$message, "\n")
    # Skip this iteration
  }, error = function(e) {
    cat("Error in iteration", i, ":", e$message, "\n")
    # Skip this iteration
  })

  if (inherits(result, "try-error")) {
    cat("Excluding iteration", i, "due to error or NAs\n")
  }
}

rownames(coefmat) <- names(summary(bmod)$coefficients$cond[,1])  #Not sure what row names would be here
coefmat <- data.frame(coefmat)
CIs_annual_encounter400 <- t(apply(coefmat,1,function(x){quantile(x,probs=c(0.025,0.975))}))



``` 


## Diagnostic plots for encounter models

```{r DHARMa plots encounters}

#200m

#Three month
encounters_mod_3month_200m_simres <- simulateResiduals(encounters_mod_3month_200m)
plot(encounters_mod_3month_200m_simres)


#Annual
encounters_mod_annual_200m_simres <- simulateResiduals(encounters_mod_annual_200m)
plot(encounters_mod_annual_200m_simres)


#400m

#Three month
encounters_mod_3month_400m_simres <- simulateResiduals(encounters_mod_3month_400m)
plot(encounters_mod_3month_200m_simres)


#Annual
encounters_mod_annual_400m_simres <- simulateResiduals(encounters_mod_annual_400m)
plot(encounters_mod_annual_200m_simres)

```


## Test for temporal autocorrelation in encounter models

```{r acf() function for encounter models}

acf(resid(encounters_mod_3month_200m))
acf(resid(encounters_mod_annual_200m))

acf(resid(encounters_mod_3month_400m))
acf(resid(encounters_mod_annual_400m))

```



## Figures

## Home Range

```{r three month spi model predictions}

####Wild Dog####

####95% home range####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. 

pred_dog95_3month_figure <- CIs_pred_dog95_3month %>%
  t() %>%
  as.data.frame() %>%
  cbind(pred_dog95_3month) %>%
  dplyr::select(x = "threemonth_spi", predicted = "mean_pred_dog95_3month", conf.low = "2.5%", conf.high = "97.5%") 

#Plot bounds (min and max of observed data)

data_figure <- df_HR %>%
  subset(Species=="African Wild Dog" & isopleth=="BB95") 

data_figure_min <-  min(data_figure$threemonth_spi) #-0.94
data_figure_max <-  max(data_figure$threemonth_spi) #1.19

#Plot

ggplot() +
  geom_line(data = pred_dog95_3month_figure, aes(x = x, y = predicted), size = 1, color = "darkturquoise") +
  xlab("Standard Precipitation Index") +
  ylab("Home Range Size in km squared (model predictions)") +
  ggtitle("Wild dog 95% home range size as a function of 3-month SPI") +
  theme_classic() +
  theme(text = element_text(size = 10)) +
  geom_ribbon(data = pred_dog95_3month_figure, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), fill = "lightblue", alpha = 0.2) +
  geom_point(data=subset(df_HR, Species=="African Wild Dog" & isopleth=="BB95"), aes(x=threemonth_spi, y=hr_area), color = "black", size = 1) +
  scale_x_continuous(limits = c(-1, 1.2)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 700))



####50% home range####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. 

pred_dog50_3month_figure <- CIs_pred_dog50_3month %>%
  t() %>%
  as.data.frame() %>%
  cbind(pred_dog50_3month) %>%
  dplyr::select(x = "threemonth_spi", predicted = "mean_pred_dog50_3month", conf.low = "2.5%", conf.high = "97.5%") 

#Plot bounds (min and max of observed data)

data_figure <- df_HR %>%
  subset(Species=="African Wild Dog" & isopleth=="BB50") 

data_figure_min <-  min(data_figure$threemonth_spi)
data_figure_max <-  max(data_figure$threemonth_spi)

#Plot
ggplot() +
  geom_line(data = pred_dog50_3month_figure, aes(x = x, y = predicted), size = 1, color = "darkturquoise") +
  xlab("Standard Precipitation Index") +
  ylab("Home Range Size in km squared (model predictions)") +
  ggtitle("Wild dog 50% home range size as a function of 3-month SPI") +
  theme_classic() +
  theme(text = element_text(size = 10)) +
  geom_ribbon(data = pred_dog50_3month_figure, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), fill = "lightblue", alpha = 0.2) +
  geom_point(data=subset(df_HR, Species=="African Wild Dog" & isopleth=="BB50"), aes(x=threemonth_spi, y=hr_area), color = "black", size = 1) +
  scale_x_continuous(limits = c(-1, 1.2)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100))


```


```{r annual SPI model predictions}

####Lion####

####95% home range####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. Making separate columns for male and female predictions so can plot separately.

pred_lion95_annual_wide <- pred_lion95_annual %>% 
  pivot_wider(
    names_from = "Sex",
    values_from = "mean_pred_lion95_annual"
  ) 
  
CI_labels <- c(rep("M",30),rep("F",30))
  
CIs_all <- CIs_pred_lion95_annual %>%
  t() %>%
  as.data.frame() %>%
  mutate(CI_labels)

CIs_male <- CIs_all %>%
  subset(CI_labels == "M") %>%
  dplyr::select("2.5%_m" = "2.5%", "97.5%_m" = "97.5%")
  
CIs_female <- CIs_all %>%
  subset(CI_labels == "F") %>%
  dplyr::select("2.5%_f" = "2.5%", "97.5%_f" = "97.5%")

CIs_all_mf <- cbind(CIs_male, CIs_female)

pred_lion95_annual_figure <- CIs_all_mf %>%
  cbind(pred_lion95_annual_wide) %>%
  dplyr::select(x = "prevyear_spi", predicted.m = "M", predicted.f = "F", conf.low.m = "2.5%_m", conf.high.m = "97.5%_m", conf.low.f = "2.5%_f", conf.high.f = "97.5%_f") 

#Plot bounds (min and max of observed data)

data_figure <- df_HR %>%
  subset(Species=="Lion" & isopleth=="BB95") 

data_figure_min <-  min(data_figure$prevyear_spi) #-0.66
data_figure_max <-  max(data_figure$prevyear_spi) #1.37

#Plot
ggplot() +
  geom_line(data = pred_lion95_annual_figure, aes(x = x, y = predicted.m), size = 1, color = "peru") +
  geom_line(data = pred_lion95_annual_figure, aes(x = x, y = predicted.f), size = 1, color = "black") +
  xlab("Standard Precipitation Index") +
  ylab("Home Range Size in km squared (model predictions)") +
  ggtitle("Lion 95% home range size as a function of annual SPI") +
  theme_classic() +
  theme(text = element_text(size = 10)) +
  geom_ribbon(data = pred_lion95_annual_figure, aes(x = x, y = predicted.m, ymin = conf.low.m, ymax = conf.high.m), fill = "goldenrod", alpha = 0.2) +
  geom_ribbon(data = pred_lion95_annual_figure, aes(x = x, y = predicted.f, ymin = conf.low.f, ymax = conf.high.f), fill = "grey", alpha = 0.2) +
  geom_point(data=subset(df_HR, Species=="Lion" & isopleth=="BB95" & Sex == "M"), aes(x=prevyear_spi, y=hr_area), color = "black", size = 1) +
  geom_point(data=subset(df_HR, Species=="Lion" & isopleth=="BB95" & Sex == "F"), aes(x=prevyear_spi, y=hr_area), color = "black", size = 1) +
  scale_x_continuous(limits = c(-0.7, 1.4)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 350))


####50% home range####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. Making separate columns for male and female predictions so can plot separately.

pred_lion50_annual_wide <- pred_lion50_annual %>% 
  pivot_wider(
    names_from = "Sex",
    values_from = "mean_pred_lion50_annual"
  ) 

CI_labels <- c(rep("M",30),rep("F",30))

CIs_all <- CIs_pred_lion50_annual %>%
  t() %>%
  as.data.frame() %>%
  mutate(CI_labels)

CIs_male <- CIs_all %>%
  subset(CI_labels == "M") %>%
  dplyr::select("2.5%_m" = "2.5%", "97.5%_m" = "97.5%")

CIs_female <- CIs_all %>%
  subset(CI_labels == "F") %>%
  dplyr::select("2.5%_f" = "2.5%", "97.5%_f" = "97.5%")

CIs_all_mf <- cbind(CIs_male, CIs_female)

pred_lion50_annual_figure <- CIs_all_mf %>%
  cbind(pred_lion50_annual_wide) %>%
  dplyr::select(x = "prevyear_spi", predicted.m = "M", predicted.f = "F", conf.low.m = "2.5%_m", conf.high.m = "97.5%_m", conf.low.f = "2.5%_f", conf.high.f = "97.5%_f") 

#Plot bounds (min and max of observed data)

data_figure <- df_HR %>%
  subset(Species=="Lion" & isopleth=="BB50") 

data_figure_min <-  min(data_figure$prevyear_spi) #-0.66
data_figure_max <-  max(data_figure$prevyear_spi) #1.37

#Plot
ggplot() +
  geom_line(data = pred_lion50_annual_figure, aes(x = x, y = predicted.m), size = 1, color = "peru") +
  geom_line(data = pred_lion50_annual_figure, aes(x = x, y = predicted.f), size = 1, color = "black") +
  xlab("Standard Precipitation Index") +
  ylab("Home Range Size in km squared (model predictions)") +
  ggtitle("Lion 50% home range size as a function of annual SPI") +
  theme_classic() +
  theme(text = element_text(size = 10)) +
  geom_ribbon(data = pred_lion50_annual_figure, aes(x = x, y = predicted.m, ymin = conf.low.m, ymax = conf.high.m), fill = "goldenrod", alpha = 0.2) +
  geom_ribbon(data = pred_lion50_annual_figure, aes(x = x, y = predicted.f, ymin = conf.low.f, ymax = conf.high.f), fill = "grey", alpha = 0.2) +
  geom_point(data=subset(df_HR, Species=="Lion" & isopleth=="BB50" & Sex == "M"), aes(x=prevyear_spi, y=hr_area), color = "black", size = 1) +
  geom_point(data=subset(df_HR, Species=="Lion" & isopleth=="BB50" & Sex == "F"), aes(x=prevyear_spi, y=hr_area), color = "black", size = 1) +
  scale_x_continuous(limits = c(-0.7, 1.4)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 50))


####Leopard####

####95% home range####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. 

pred_leopard95_annual_figure <- CIs_pred_leopard95_annual %>%
  t() %>%
  as.data.frame() %>%
  cbind(pred_leopard95_annual) %>%
  dplyr::select(x = "prevyear_spi", predicted = "mean_pred_leopard95_annual", conf.low = "2.5%", conf.high = "97.5%") 

#Plot bounds (min and max of observed data)

data_figure <- df_HR %>%
  subset(Species=="Leopard" & isopleth=="BB95") 

data_figure_min <-  min(data_figure$prevyear_spi) #-0.49
data_figure_max <-  max(data_figure$prevyear_spi) #1.37

#Plot
ggplot() +
  geom_line(data = pred_leopard95_annual_figure, aes(x = x, y = predicted), size = 1, color = "darkgreen") +
  xlab("Standard Precipitation Index") +
  ylab("Home Range Size in km squared (model predictions)") +
  ggtitle("Leopard 95% home range size as a function of annual SPI") +
  theme_classic() +
  theme(text = element_text(size = 10)) +
  geom_ribbon(data = pred_leopard95_annual_figure, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), fill = "darkseagreen", alpha = 0.2) +
  geom_point(data=subset(df_HR, Species=="Leopard" & isopleth=="BB95"), aes(x=prevyear_spi, y=hr_area), color = "black", size = 1) +
  scale_x_continuous(limits = c(-0.5, 1.4)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 200))



####50% home range####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. 

pred_leopard50_annual_figure <- CIs_pred_leopard50_annual %>%
  t() %>%
  as.data.frame() %>%
  cbind(pred_leopard50_annual) %>%
  dplyr::select(x = "prevyear_spi", predicted = "mean_pred_leopard50_annual", conf.low = "2.5%", conf.high = "97.5%") 

#Plot bounds (min and max of observed data)
data_figure <- df_HR %>%
  subset(Species=="Leopard" & isopleth=="BB50") 

data_figure_min <-  min(data_figure$prevyear_spi)
data_figure_max <-  max(data_figure$prevyear_spi)

#Plot 
ggplot() +
  geom_line(data = pred_leopard50_annual_figure, aes(x = x, y = predicted), size = 1, color = "darkgreen") +
  xlab("Standard Precipitation Index") +
  ylab("Home Range Size in km squared (model predictions)") +
  ggtitle("Leopard 50% home range size as a function of annual SPI") +
  theme_classic() +
  theme(text = element_text(size = 10)) +
  geom_ribbon(data = pred_leopard50_annual_figure, aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), fill = "darkseagreen", alpha = 0.2) +
  geom_point(data=subset(df_HR, Species=="Leopard" & isopleth=="BB50"), aes(x=prevyear_spi, y=hr_area), color = "black", size = 1) +
  scale_x_continuous(limits = c(-0.5, 1.4)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40))


```


## Overlap

```{r beta plots depicting amount of overlap}

####95% overlap annual beta####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. 

CIs_pred_overlap95_beta_annual_figure <- CIs_pred_overlap95_beta_annual %>%
  t() %>%
  as.data.frame() %>%
  cbind(pred_overlap95_beta_annual) %>%
  dplyr::select(dyad_species, x = "prevyear_spi", predicted = "mean_pred_overlap95_beta_annual", conf.low = "2.5%", conf.high = "97.5%") 

#Plot bounds (min and max of observed data)
data_figure <- overlap_95_beta %>%
  subset(dyad_species=="Cheetah-Lion") 

data_figure_min <-  min(data_figure$prevyear_spi) #-0.66
data_figure_max <-  max(data_figure$prevyear_spi) #0.16

#Plot
ggplot() +
  geom_line(data = subset(CIs_pred_overlap95_beta_annual_figure, dyad_species == "Cheetah-Lion"), aes(x = x, y = predicted, color = dyad_species), size = 1) +
  xlab("Standard Precipitation Index") +
  ylab("Overlap coefficient (model predictions)") +
  ggtitle("Cheetah-Lion 95% home range overlap as a function of annual SPI (beta)") +
  theme_classic() +
  geom_ribbon(data = subset(CIs_pred_overlap95_beta_annual_figure, dyad_species == "Cheetah-Lion"), aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = dyad_species), fill = "grey", alpha = 0.2) +
  theme(text = element_text(size = 10)) + 
  scale_color_brewer(palette="Set2") +
  geom_point(data=subset(overlap_95_beta, dyad_species=="Cheetah-Lion"), aes(x=prevyear_spi, y=overlap), color = "black", size = 1) +
  scale_x_continuous(limits = c(-0.7, 0.25)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.55))


####50% overlap annual beta####

#Reformatting dataframes with predictions and bootstrap CIs on predictions. 

CIs_pred_overlap50_beta_annual_figure <- CIs_pred_overlap50_beta_annual %>%
  t() %>%
  as.data.frame() %>%
  cbind(pred_overlap50_beta_annual) %>%
  dplyr::select(dyad_species, x = "prevyear_spi", predicted = "mean_pred_overlap50_beta_annual", conf.low = "2.5%", conf.high = "97.5%") 

#Plot bounds (min and max of observed data)

data_figure <- overlap_50_beta %>%
  subset(dyad_species=="Leopard-Lion") 

data_figure_min <-  min(data_figure$prevyear_spi) #-0.49
data_figure_max <-  max(data_figure$prevyear_spi) #1.37

#Plot
ggplot() +
  geom_line(data = subset(CIs_pred_overlap50_beta_annual_figure, dyad_species == "Leopard-Lion"), aes(x = x, y = predicted, color = dyad_species), size = 1) +
  xlab("Standard Precipitation Index") +
  ylab("Overlap coefficient (model predictions)") +
  ggtitle("Leopard-Lion 50% home range overlap as a function of annual SPI (beta)") +
  theme_classic() +
  geom_ribbon(data = subset(CIs_pred_overlap50_beta_annual_figure, dyad_species == "Leopard-Lion"), aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high, group = dyad_species), fill = "grey", alpha = 0.2) +
  theme(text = element_text(size = 10)) + 
  scale_color_brewer(palette="Set2") +
  geom_point(data=subset(overlap_50_beta, dyad_species=="Leopard-Lion"), aes(x=prevyear_spi, y=overlap), color = "black", size = 1) +
  scale_x_continuous(limits = c(-0.5, 1.5)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.25))

```
